Low Complexity Adaptive Beamformer\\ for Active Sonar Imaging

### 2015-10-05 LCAforActiveSonarImaging/lca.tex
la2pdf commit - 2015:10:05	14:02:50	(Mon 5.Oct)
la2pdf commit - 2015:10:05	14:33:37	(Mon 5.Oct)

We show that a robust MVDR implementation typically chooses approximately symmetric windows with maximum sidelobe levels between that of the rectangular and Hamming window. We then set up LCA to use Kaiser windows with similar responses to those of MVDR, and apply various amounts of steering. We find that when Steering to -3\,dB width of the window. This lead to a predictable resolution gain of . design LCA's window database with windows that resembles  constrained to work in active sonar imaging the typical window responses LCA is allowed to choose from windows that are typical solutions found by the minimum variance distortionless response (MVDR) method.

@@

\newpage
\section{Receive Beamforming}\label{sec:beamforming}

>>>>

We show that a robust MVDR implementation typically chooses symmetric windows with responses in between that of the rectangular and Hamming window. When allowing LCA to choose from similar use Kaiser windows with similar responses to those of MVDR, and apply various amounts of steering. We find that when Steering to -3\,dB width of the window. This lead to a predictable resolution gain of . design LCA's window database with windows that resembles  constrained to work in active sonar imaging the typical window responses LCA is allowed to choose from windows that are typical solutions found by the minimum variance distortionless response (MVDR) method.

@@

\section{Receive Beamforming}\label{sec:beamforming}
